---
title: "fars Documentation"
author: "Nate Heng"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

#fars

The fars package manipulates [US National Highway Traffic Safety Administration's Fatality Analysis Reporting System](https://www.nhtsa.gov/Data/Fatality-Analysis-Reporting-System-(FARS)) data.  The years 2013, 2014, and 2015 are available upon download of this package.

The *fars_summarize_years* function shown below will create a dataframe with n columns and 12 rows.  The columns represent the years input as a parameter and the rows represent the 12 months of the year.  The values within the data frame represent the total number of observations found for each month/year combination.  The example uses the years available with the package.

```{r}
library(fars)
fars_summarize_years(c(2013,2014,2015))
```

The *fars_map_state* function shown below will create a map of observations (fatal accidents) that have occurred in a given state during a specified year.  Only one year and state may be entered.  The below is an example for LA in 2013.

```{r}
fars_map_state(22,2013)
```
